---
title: "SPAN 2 Clot Study - Feasibility"
author: "Marcio Diniz, Karni Bedirian, Shu-Hsiang Wang"
date: "`r format(Sys.time(), '%d %B, %Y')`"
format: 
  html:
    toc: true
    toc-depth: 5
    toc-location: left
    column: page-right
    self-contained: true
    echo: true
    code-fold: true
    warning: false
    message: false
---

```{r}
source("00_utils.R") 
load("results/span2_clotstudy_p3_feasibility_descriptive_analysis.Rdata")
```


# Enrolled

::: {.panel-tabset}
## Overall


```{r}
tab <- tables$enrolled$overall

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Enrolled Population"
  ) 
```

## Sex
```{r}
tab <- tables$enrolled$sex

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Enrolled Population"
  ) 
```

## Site
```{r}
tab <- tables$enrolled$site

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Enrolled Population"
  ) 

```


:::

# Ineligible for Randomization

::: {.panel-tabset}
## Overall


```{r}
tab <- tables$ineligible_for_randomization$overall

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Ineligible for Randomization Population"
  ) 
```

## Sex
```{r}
tab <- tables$ineligible_for_randomization$sex

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Ineligible for Randomization Population"
  ) 
```

## Site
```{r}
tab <- tables$ineligible_for_randomization$site

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Ineligible for Randomization Population"
  ) 

```

:::


# ITT

::: {.panel-tabset}
## Overall


```{r}
tab <- tables$itt$overall

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - ITT Population"
  ) 
```

## Sex
```{r}
tab <- tables$itt$sex

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - ITT Population"
  ) 
```

## Site
```{r}
tab <- tables$itt$site

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - ITT Population"
  ) 
```

## Treatment
```{r}
tab <- tables$itt$txas_reperfusion

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - ITT Population"
  ) 
```

## Clot Length
```{r}
tab <- tables$itt$clot_length

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - ITT Population"
  ) 
```

:::

<!-- # Exclusion from Treatment -->

<!-- ::: {.panel-tabset} -->
<!-- ## Overall -->


<!-- ```{r} -->
<!-- tab <- tables$exclusion_from_treatment$overall -->

<!-- nt_format(tab) |> -->
<!--   tab_header( -->
<!--     title = "Descriptive Analysis - Exclusion from Treatment Population" -->
<!--   ) -->
<!-- ``` -->

<!-- ## Sex -->
<!-- ```{r} -->
<!-- tab <- tables$exclusion_from_treatment$sex -->

<!-- nt_format(tab) |> -->
<!--   tab_header( -->
<!--     title = "Descriptive Analysis - Exclusion from Treatment Population" -->
<!--   ) -->
<!-- ``` -->

<!-- ## Site -->
<!-- ```{r} -->
<!-- tab <- tables$exclusion_from_treatment$site -->

<!-- nt_format(tab) |> -->
<!--   tab_header( -->
<!--     title = "Descriptive Analysis - Exclusion from Treatment Population" -->
<!--   ) -->

<!-- ``` -->

<!-- ## Treatment -->
<!-- ```{r} -->
<!-- tab <- tables$exclusion_from_treatment$txas_tx_group -->

<!-- nt_format(tab) |> -->
<!--   tab_header( -->
<!--     title = "Descriptive Analysis - Exclusion from Treatment Population" -->
<!--   ) -->
<!-- ``` -->


<!-- ::: -->

# Procedural Dropout

::: {.panel-tabset}
## Overall


```{r}
tab <- tables$procedural_dropout$overall

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Procedural Dropout Population"
  ) 
```

## Sex
```{r}
tab <- tables$procedural_dropout$sex

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Procedural Dropout Population"
  ) 
```

## Site
```{r}
tab <- tables$procedural_dropout$site

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Procedural Dropout Population"
  )

```

## Treatment
```{r}
tab <- tables$procedural_dropout$txas_reperfusion

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Procedural Dropout Population"
  ) 
```

## Clot Length
```{r}
tab <- tables$procedural_dropout$clot_length

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Procedural Dropout Population"
  ) 
```
:::


# mITT

::: {.panel-tabset}
## Overall


```{r}
tab <- tables$mitt$overall

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - mITT Population"
  ) 
```

## Sex
```{r}
tab <- tables$mitt$sex

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - mITT Population"
  ) 
```

## Site
```{r}
tab <- tables$mitt$site

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - mITT Population"
  ) 
```

## Treatment

```{r}
tab <- tables$mitt$txas_reperfusion

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - mITT Population"
  ) 
```


## Clot Length
```{r}
tab <- tables$mitt$clot_length

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - mITT Population"
  ) 
```
:::


# Partial Treatment

::: {.panel-tabset}
## Overall


```{r}
tab <- tables$partial_treatment$overall

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Partial Treatment Population"
  ) 
```

## Sex
```{r}
tab <- tables$partial_treatment$sex

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Partial Treatment Population") 
```

## Site
```{r}
tab <- tables$partial_treatment$site

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Partial Treatment Population"
  ) 
```

## Treatment
```{r}
tab <- tables$partial_treatment$txas_reperfusion

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Partial Treatment Population") 
```

## Clot Length
```{r}
tab <- tables$partial_treatment$clot_length

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Partial Treatment Population"
  ) 
```

:::


# Per Protocol

::: {.panel-tabset}
## Overall


```{r}
tab <- tables$pp$overall

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Fully Treated Population")
```

## Sex
```{r}
tab <- tables$pp$sex

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Fully Treated Population"
  )
```

## Site
```{r}
tab <- tables$pp$site

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Fully Treated Population"
  )

```

## Treatment

```{r}
tab <- tables$pp$txas_reperfusion

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Fully Treated Population"
  ) 
```


## Clot Length
```{r}
tab <- tables$pp$clot_length

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Fully Treated Population"
  ) 
```

:::


# Loss to follow-up

::: {.panel-tabset}
## Overall


```{r}
tab <- tables$loss_followup$overall

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Loss to follow-up Population"
  ) 
```

## Sex
```{r}
tab <- tables$loss_followup$sex

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Loss to follow-up Population"
  ) 
```

## Site
```{r}
tab <- tables$loss_followup$site

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Loss to follow-up Population"
  ) 
```

## Treatment
```{r}
tab <- tables$loss_followup$txas_reperfusion

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Loss to follow-up Population"
  ) 
```

## Clot Length
```{r}
tab <- tables$loss_followup$clot_length

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Loss to follow-up Population"
  ) 
```
:::

# Full Data Population

::: {.panel-tabset}
## Overall


```{r}
tab <- tables$full_data$overall

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Full Data Population"
  ) 
```

## Sex
```{r}
tab <- tables$full_data$sex

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Full Data Population"
  ) 
```

## Site
```{r}
tab <- tables$full_data$site

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Full Data Population"
  ) 
```

## Treatment
```{r}
tab <- tables$full_data$txas_reperfusion

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Full Data Population"
  ) 
```

## Clot Length
```{r}
tab <- tables$full_data$clot_length

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Full Data Population"
  ) 
```
:::
