---
title: "SPAN 2 Clot Study - Day 30 Corner Test"
subtitle: "PP Population"
author: "Marcio Diniz, Karni Bedirian, Shu-Hsiang Wang"
date: "`r format(Sys.time(), '%d %B, %Y')`"
format: 
  html:
    toc: true
    toc-depth: 5
    toc-location: left
    column: page-right
    self-contained: true
    echo: true
    code-fold: true
    warning: false
    message: false
---

```{r}
source("00_utils.R") 
load("results/span2_clotstudy_p3_d30_corner_test_analysis_pp.Rdata")
```


# Feasibility

::: {.panel-tabset}
## Overall


```{r}
tab <- tables$feasibility$overall

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Corner Test - Feasibility"
  ) 
```


## Site
```{r}
tab <- tables$feasibility$site

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Corner Test - Feasibility"
  ) 

```

## Sex
```{r}
tab <- tables$feasibility$sex

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Corner Test - Feasibility"
  ) 
```

## Treatment
```{r}
tab <- tables$feasibility$txas_reperfusion

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Corner Test - Feasibility"
  ) 
```

## Clot length
```{r}
tab <- tables$feasibility$clot_length

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Corner Test - Feasibility"
  ) 
```

:::


# Outcomes

## Definitions

**Alternative Corner Test Index** = $\displaystyle\frac{\mbox{Abs(Left Turns - Right Turns)}}{\mbox{Left Turns + Right Turns}}$

## Tables

::: {.panel-tabset}

### Overall

```{r}
tab <- tables$outcome$overall

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Alternative Corner Test Index"
  ) 
```

### Treatment

```{r}
tab <- tables$outcome$txas_reperfusion

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Alternative Corner Test Index by treatment"
  ) 
```

### Sex

::: {.panel-tabset}

#### Female
```{r}
tab <- tables$outcome$sex$f

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Alternative Corner Test Index by treatment",
    subtitle = "Sex: Female"
  ) 
```

#### Male
```{r}
tab <- tables$outcome$sex$m

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Alternative Corner Test Index by treatment",
    subtitle = "Sex: Male"
  ) 
```
:::

### Site

::: {.panel-tabset}

#### AG
```{r}
tab <- tables$outcome$site$ag

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Alternative Corner Test Index by treatment",
    subtitle = "Site: AG"
  ) 
```

#### DK
```{r}
tab <- tables$outcome$site$dk

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Alternative Corner Test Index by treatment",
    subtitle = "Site: DK"
  ) 
```

#### IW
```{r}
tab <- tables$outcome$site$iw

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Alternative Corner Test Index by treatment",
    subtitle = "Site: IW"
  ) 
```

#### MG
```{r}
tab <- tables$outcome$site$mg

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Alternative Corner Test Index by treatment",
    subtitle = "Site: MG"
  ) 
```

#### SD
```{r}
tab <- tables$outcome$site$sd

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Alternative Corner Test Index by treatment",
    subtitle = "Site: SD"
  ) 
```

#### YL
```{r}
tab <- tables$outcome$site$yl

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Alternative Corner Test Index by treatment",
    subtitle = "Site: YL"
  ) 
```

:::

### Clot Length

::: {.panel-tabset}

#### 3cm
```{r}
tab <- tables$outcome$clot_length$cl3

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Alternative Corner Test Index by treatment",
    subtitle = "Clot Length: 3cm"
  ) 
```

#### 4cm
```{r}
tab <- tables$outcome$clot_length$cl4

nt_format(tab) |>
  tab_header(
    title = "Descriptive Analysis - Alternative Corner Test Index by treatment",
    subtitle = "Clot Length: 4cm"
  ) 
```
:::


:::


## Plots

::: {.panel-tabset}

### Treatment

::: {.panel-tabset}

#### Baseline
```{r}
plots$outcome$overall$txas_reperfusion$d0
```

#### Day 7
```{r}
plots$outcome$overall$txas_reperfusion$d7
```

#### Day 30
```{r}
plots$outcome$overall$txas_reperfusion$d30
```

:::

### Site

::: {.panel-tabset}

#### Baseline
```{r, fig.width=12, fig.height=8}
plots$outcome$overall$site$d0
```

#### Day 7
```{r, fig.width=12, fig.height=8}
plots$outcome$overall$site$d7
```

#### Day 30
```{r, fig.width=12, fig.height=8}
plots$outcome$overall$site$d30
```

:::

### Sex

::: {.panel-tabset}

#### Baseline
```{r, fig.width=8, fig.height=4}
plots$outcome$overall$sex$d0
```

#### Day 7
```{r, fig.width=8, fig.height=4}
plots$outcome$overall$sex$d7
```

#### Day 30
```{r, fig.width=8, fig.height=4}
plots$outcome$overall$sex$d30
```

:::


### Clot Length

::: {.panel-tabset}

#### Baseline
```{r, fig.width=8, fig.height=4}
plots$outcome$overall$clot_length$d0
```

#### Day 7
```{r, fig.width=8, fig.height=4}
plots$outcome$overall$clot_length$d7
```

#### Day 30
```{r, fig.width=8, fig.height=4}
plots$outcome$overall$clot_length$d30
```

:::

:::

## Test of Hypotheses 

`r interpretation$model`

`r interpretation$treat`

`r interpretation$imp`

::: {.panel-tabset}

### No missing data imputation

::: {.panel-tabset}

#### Interaction

```{r}
plots$pim$noimputation$interaction
```


#### Overall

```{r}
tab <- bind_rows(tables$pim$noimputation$overall$txas_reperfusion,
                 tables$pim$noimputation$overall$clot_length)
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
::: {.panel-tabset}
###### Treatment

```{r }
plots$pim$noimputation$overall$txas_reperfusion
```

###### Clot Length

```{r }
plots$pim$noimputation$overall$clot_length
```
:::

##### Full Output

```{r}
tab <- tables$pim$noimputation$overall$full_output
gt(tab) 
```

#### CL3

```{r}
tab <- tables$pim$noimputation$cl3$txas_reperfusion 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
```{r }
plots$pim$noimputation$cl3
```

##### Full Output

```{r}
tab <- tables$pim$noimputation$cl3$full_output
gt(tab) 
```

#### CL4

```{r}
tab <- tables$pim$noimputation$cl4$txas_reperfusion 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
```{r }
plots$pim$noimputation$cl4
```

##### Full Output

```{r}
tab <- tables$pim$noimputation$cl4$full_output
gt(tab) 
```

:::

### Missing data imputation - Worst Score Overall

::: {.panel-tabset}

#### Interaction

```{r}
plots$pim$imputation_ws_overall$interaction
```


#### Overall

```{r}
tab <- bind_rows(tables$pim$imputation_ws_overall$overall$txas_reperfusion,
                 tables$pim$imputation_ws_overall$overall$clot_length) 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
::: {.panel-tabset}
###### Treatment

```{r }
plots$pim$imputation_ws_overall$overall$txas_reperfusion
```

###### Clot Length

```{r }
plots$pim$imputation_ws_overall$overall$clot_length
```
:::

##### Full Output

```{r}
tab <- tables$pim$imputation_ws_overall$overall$full_output
gt(tab) 
```

#### CL3

```{r}
tab <- tables$pim$imputation_ws_overall$cl3$txas_reperfusion 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
```{r }
plots$pim$imputation_ws_overall$cl3
```

##### Full Output

```{r}
tab <- tables$pim$imputation_ws_overall$cl3$full_output
gt(tab) 
```

#### CL4

```{r}
tab <- tables$pim$imputation_ws_overall$cl4$txas_reperfusion 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
```{r }
plots$pim$imputation_ws_overall$cl4
```

##### Full Output

```{r}
tab <- tables$pim$imputation_ws_overall$cl4$full_output
gt(tab) 
```

:::

### Missing data imputation - Worst Score CLS

::: {.panel-tabset}

#### Interaction

```{r}
plots$pim$imputation_ws_cls$interaction
```


#### Overall

```{r}
tab <- bind_rows(tables$pim$imputation_ws_cls$overall$txas_reperfusion,
                 tables$pim$imputation_ws_cls$overall$clot_length) 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
::: {.panel-tabset}
###### Treatment

```{r }
plots$pim$imputation_ws_cls$overall$txas_reperfusion
```

###### Clot Length

```{r }
plots$pim$imputation_ws_cls$overall$clot_length
```
:::

##### Full Output

```{r}
tab <- tables$pim$imputation_ws_cls$overall$full_output
gt(tab) 
```

#### CL3

```{r}
tab <- tables$pim$imputation_ws_cls$cl3$txas_reperfusion 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
```{r }
plots$pim$imputation_ws_cls$cl3
```

##### Full Output

```{r}
tab <- tables$pim$imputation_ws_cls$cl3$full_output
gt(tab) 
```

#### CL4

```{r}
tab <- tables$pim$imputation_ws_cls$cl4$txas_reperfusion 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
```{r }
plots$pim$imputation_ws_cls$cl4
```

##### Full Output

```{r}
tab <- tables$pim$imputation_ws_cls$cl4$full_output
gt(tab) 
```

:::

### Missing data imputation - Worst Score CLST

::: {.panel-tabset}

#### Interaction

```{r}
plots$pim$imputation_ws_clst$interaction
```


#### Overall

```{r}
tab <- bind_rows(tables$pim$imputation_ws_clst$overall$txas_reperfusion,
                 tables$pim$imputation_ws_clst$overall$clot_length) 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
::: {.panel-tabset}
###### Treatment

```{r }
plots$pim$imputation_ws_clst$overall$txas_reperfusion
```

###### Clot Length

```{r }
plots$pim$imputation_ws_clst$overall$clot_length
```
:::
##### Full Output

```{r}
tab <- tables$pim$imputation_ws_clst$overall$full_output
gt(tab) 
```

#### CL3

```{r}
tab <- tables$pim$imputation_ws_clst$cl3$txas_reperfusion 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
```{r }
plots$pim$imputation_ws_clst$cl3
```

##### Full Output

```{r}
tab <- tables$pim$imputation_ws_clst$cl3$full_output
gt(tab) 
```

#### CL4

```{r}
tab <- tables$pim$imputation_ws_clst$cl4$txas_reperfusion 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
```{r }
plots$pim$imputation_ws_clst$cl4
```

##### Full Output

```{r}
tab <- tables$pim$imputation_ws_clst$cl4$full_output
gt(tab) 
```

:::

### Missing data imputation - Multiple Imputation

::: {.panel-tabset}

#### Interaction

```{r}
plots$pim$imputation_mi$interaction
```


#### Overall

```{r}
tab <- bind_rows(tables$pim$imputation_mi$overall$txas_reperfusion,
                 tables$pim$imputation_mi$overall$clot_length) 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
::: {.panel-tabset}
###### Treatment

```{r }
plots$pim$imputation_mi$overall$txas_reperfusion
```

###### Clot Length

```{r }
plots$pim$imputation_mi$overall$clot_length
```
:::

##### Full Output

```{r}
tab <- tables$pim$imputation_mi$overall$full_output
gt(tab) 
```

#### CL3

```{r}
tab <- tables$pim$imputation_mi$cl3$txas_reperfusion 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
```{r }
plots$pim$imputation_mi$cl3
```

##### Full Output

```{r}
tab <- tables$pim$imputation_mi$cl3$full_output
gt(tab) 
```

#### CL4

```{r}
tab <- tables$pim$imputation_mi$cl4$txas_reperfusion 
gt(tab) |> 
  tab_header(
    title = "Relative Effect - Probabilistic Index Model"
  ) |>
  tab_footnote(
    footnote = footnote$ci,
    locations = cells_column_labels(columns = "PI (95% CI)")
  ) |>
  tab_footnote(
    footnote = footnote$pvals,
    locations = cells_column_labels(columns = "p value")
  ) |>
  tab_footnote(
    footnote = footnote$pi
  )
```

##### Plot
```{r }
plots$pim$imputation_mi$cl4
```

##### Full Output

```{r}
tab <- tables$pim$imputation_mi$cl4$full_output
gt(tab) 
```

:::

### Summary

::: {.panel-tabset}

#### Overall

::: {.panel-tabset}

##### Treatment
```{r}
plots$summary$tx$overall
```

##### Clot Length
```{r}
plots$summary$clot_length$overall
```

:::

#### CL3

```{r}
plots$summary$cl3
```

#### CL4

```{r}
plots$summary$cl4
```

:::

:::